CUNY SPSS Data Science Math Homework 2

### 2018-07-20 data-science-math/Homework 2.Rmd
More progress on week 2

```{r setup, include=FALSE}
library(pander)
knitr::opts_chunk$set(echo = TRUE)
```

@@

@@

@@

>>>>

```{r setup, include=FALSE}
library(pander)
library(tidyr)
library(gtools)
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r}
drinks <- c(1,2,3,4,5,6)
sandwiches <- c(1,2,3,4,5)
chips <- c(1,2,3)

q11_data <- tidyr::crossing(drinks, sandwiches) %>%
  tidyr::crossing(., chips)
nrow(q11_data)
```

@@

$$ P(n) = n! \Rightarrow P(5)=5! = 5 \times 4 \times 3 \times 2 \times 1 = 120 $$
```{r}
factorial(5)

patients <- c(1,2,3,4,5)
q12_data <- permutations(length(patients), length(patients), patients)
nrow(q12_data)
```

@@

$$ C(n,r) = \frac{n!}{r!(n-r)!} \Rightarrow C(8,5) = \frac{8!}{5!(8-5)!} =  \frac{40320}{120\cdot 3!} = \frac{40320}{120\cdot 6} = \frac{40320}{720} = 56$$

```{r}
q13_data <- combinations(8,5)
nrow(q13_data)
```
